Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed a path
Fixed some section headings

# Save to github
ggsave(filename = "publications_per_year.tiff",
       plot = publications_per_year_plot,
       path = figs_dir
       )

@@

## Collaboration types (aggregated)
```{r}
#' Count by collaboration types and make a bar plot
studies_per_collab_type <- compact_data_with_citation_keys_no_fmd %>%
    count(collab_type, sort = TRUE) %>% 
    arrange(desc(n)) %>% 
    adorn_totals() %>% 
    adorn_percentages(denominator = 'col') %>% 
    adorn_pct_formatting() %>% 
    adorn_ns()

>>>>

# Save to github
ggsave(filename = "publications_per_year.tiff",
       plot = publications_per_year_plot,
       path = gh_figs_dir
       )

@@

## Analysis of collaboration type compositions

### Aggregated
```{r}
#' Count by collaboration types and make a bar plot
studies_per_collab_type <- compact_data_with_citation_keys_no_fmd %>%
    count(collab_type, sort = TRUE) %>% 
    arrange(desc(n)) %>% 
    adorn_totals() %>% 
    adorn_percentages(denominator = 'col') %>% 
    adorn_pct_formatting() %>% 
    adorn_ns()
